GMSE: a general tool for management strategy evaluation

### 2017-09-14 notebook/presentation/GMSE_presentation.Rmd
New scattered slides

@@

Need some background on management

@@

@@

@@

@@

>>>>

##

![](wildlife_conflict_sm.jpg)

<center>
**Image**: [Public domain](https://commons.wikimedia.org/wiki/File:Human-wildlife_conflict.jpg)
</center>

- People with strongly held views clash over objectives
- Negative effect on sustainability, biodiversity, and human livelihood

## Game theory: conflict and cooperation

<div class="columns-2">

- Formalisation and study of conflict and cooperation between rational decision-makers
- Broadly encompasses combinatorial games (e.g., tic-tac-toe, chess) and evolutionary invasion analysis (adaptive dynamics)
- Compatibile with agent-based modelling

![](payoff_matrix_sm.png)

</div>
<hr>

[Adami et al. (2016) Phys. Life. Rev. 19:1-26](http://dx.doi.org/10.1016/j.plrev.2016.08.015)

## {.smaller}

<div class="columns-2">

![Public license](US_USSR_nukes_sm.png).

![Wilkinson 1990](Wilkinson1990_sm.png).

![Isaacdm](penalty_sm.png).

![Dennig](brexit_sm.png).

</div>

**Images:** (1) [Public license](https://commons.wikimedia.org/wiki/File:US_and_USSR_nuclear_stockpiles.svg), (2) [Wilkinson 1990](https://projects.ncsu.edu/project/evoresources/Evolutionary%20medicine/Unitsofselection%20DM%20copy/wilkinson-foodsharing.pdf), (3) [Isaacdm](https://commons.wikimedia.org/wiki/File:PhysicsofPenalty.JPG?uselang=en-gb), (4) [Public license](http://www.publicdomainpictures.net/view-image.php?image=180560&picture=brexit-referendum-uk)

## Conflict in conservation

Game theory provides a natural framework for addressing issues of cooperation and conflict in conservation.

- Game theory can be used to understand stake-holder decision making ([Kark et al. 2015 *Curr. Opin. Environ. Sustainability* **12**:12-24]()).

- Game-theoretic models can suggest novel management strategies ([Colvan et al. 2011 *Biol. Conserv.* **144**:1246-1253](http://dx.doi.org/10.1016/j.biocon.2010.10.028); [Tilman et al. 2016 *Theor. Ecol.*](http://link.springer.com/article/10.1007%2Fs12080-016-0318-8)).

- Game theory can consider multiple management objectives simultaneously ([Lee 2012 *Chemosphere* **87**:608-613](http://dx.doi.org/10.1016/j.chemosphere.2012.01.014)).

Nils points out that typical game theory assumes that

- pay-offs are known and fixed
- Actions are clear and always available
- Players behave rationally
- Game rules are known to all
- There is a clear rank order of outcomes

@@

Resolving conflicts between food security and biodiversity conservation under uncertainty

<div class = "columns-2">

![](confoobio_sans.png)

- How to solve conflict
- What leads to conflict
- Impact on sustainability

All of the above are characterised by uncertainty

</div>

<!--- Get the ERC logo and EU flag in here? --->

@@

- Confoobio brings in a game-theoretic perspective to this

@@

## One run

@@

<div class = "columns-2">

![](GMSE_Logo_Goose_300.png)

</div>

@@

- Use some data from Jeremy's paper?
